---
title: "Geo-Genius: Unveil the Location"
author: "Andrea De Angelis"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In this exercise, we'll use the `httr` and `jsonlite` packages in R to make an HTTP request to the OpenCage Geocoding API, which provides latitude and longitude coordinates for a given address. The exercise demonstrates how to make a GET request, parse the JSON response, and extract relevant information.

Objective: Determine the latitude and longitude of a given address using the OpenCage Geocoding API.

# Install and load the packages

Install and load the `httr` and `jsonlite` pakcages. 

```{r}
library("httr"); library("jsonlite")
```

# Sign up for a free OpenCage API key

The link is available here: https://opencagedata.com/api 

```{r}
browseURL(url = "https://opencagedata.com/api")
api_key <- rstudioapi::askForPassword()
base_url <- "https://api.opencagedata.com/geocode/v1/json"
```

# Define an address

```{r}
address <- "Frohburgstrasse 3, 6002 Luzern"
```

# Make a GET request

```{r}
geocoding_response <- httr::GET(url = base_url, 
                                query = list(key = api_key, q = address))
```

# Check the status code

```{r}
http_status(geocoding_response)

# Something more elaborate that could be used in a personalized application:
if (http_status(geocoding_response)$category != "Success") {
  stop("The API request failed with status code: ", http_status(geocoding_response)$status_code)
}

```

# Parse JSON and display

```{r}
# Extract the content from the response object using the `httr::content()` function. 

# Eventually use rsonlite::fromJSON()
r_json <- fromJSON(httr::content(geocoding_response, as = "text"))

# Or just parse the content
geocoding_data <- httr::content(geocoding_response)

# Check out how much info is returned!
str(geocoding_data$results, 2)
geocoding_data$results[[1]]$annotations$currency$symbol   # The currency of the address
geocoding_data$results[[1]]$annotations$flag              # The flag of the address

# We actually got five places at this address:
geocoding_data$results[[1]]$formatted
geocoding_data$results[[5]]$formatted

# Get latitude and longitude of the University:
latitude <- geocoding_data$results[[1]]$geometry$lat[1]
longitude <- geocoding_data$results[[1]]$geometry$lng[1]

cat("Latitude: ", latitude, "\nLongitude: ", longitude)
```

